\section{Conducted Survey}

Even though this thesis focuses on developing a prototype mainly focused on children, also parents and teachers participated in it.
The game's future development counts on developing more features to include these user groups in the children's education.

Articles mentioned in the introduction also analyzed some use-cases of gamification in education or educational games.
These studies have been analyzed, and the conducted survey follows and considers their results. 

The primary purpose of the conducted survey for this thesis was to understand what some children, their parents, and teachers think and would make them motivated in a gamified game.

The survey recognizes three participant roles: a child, a parent, and a teacher.
Each role has a modified set of questions.

\subsection*{Questions asked only to children}

\begin{enumerate}
    \item What (non-educational) games do you usually play and why? What is your motivation for playing them? (Open-ended question.)
    \item Do you like receiving points as a reward for completing tasks? (Closed-ended question.)
    \item Do you like rankings in educational games? (Closed-ended question.)
    \item Would you like an advanced final task as a challenge? (Closed-ended question.)
    \item What is your primary motivation to play an educational game? (Open-ended question.)
\end{enumerate}

\subsection*{Questions asked to children, parents, and teachers}

\begin{enumerate}
    \item What aspects or mechanics are important in an educational game according to you? ((Closed-ended question with options: a game; a story; study materials; an explanation.)
    \item Do you (or your children/students) use any educational application or game? (Closed-ended question with options: Duolingo, Khan Academy, Minecraft, Scratch, other.)
    \item What experiences do you have with educational applications or games. What aspects do you like the most, what don't you like? (Open-ended question.)
    \item What would you appreciate most in an educational game? (Open-ended question.) 
\end{enumerate}

\subsection*{Questions asked only to parents and teachers}

\begin{enumerate}
    \item What is important to you? (Closed-ended question with options: progress monitoring; checking the results; ratings and comparison with other players; planning tasks for children to practice; an option to change child's settings.) 
\end{enumerate}
