\begin{conclusion}

This thesis aimed to develop an educational game for teaching programming, which focuses primarily on young people and uses gamification concepts.
A survey was conducted, followed by an analysis of functional and non-functional requirements.
Based on the analysis, research on existing similar games and applications that can be used to teach programming was made.
According to the analysis and research, the design of such a game was done.
That was inspired by the advantages of the compared software, which tries to solve their shortcomings.
According to the design, the game was implemented and evaluated based on usability testing.

When designing the implemented game \myAppName{}, the architecture Clean Architecture was chosen, which inspires the implementation parts mainly to the easy extensibility and reusability of the code.
The Flutter framework was chosen to implement the client part of the game as a cross-platform framework suitable for software development on mobile devices, desktops, and websites.
ASP.NET Web Api technology with the use of the C\# language was chosen to implement the server part of the game, which, thanks to its supporting technologies, enables the creation of high-quality and robust implementation.
The PostgreSQL relational database was selected as the database.
Based on the design, a user interface was created that takes care of this education-first game's understandable and straightforward appearance.

\section{Acquired Experience}

I gained a lot of valuable experience from this project.
I've explored both paths that work and paths that don't.
In terms of experience with client software implementation, I successfully got acquainted with and implemented the user interface with a declarative approach, which the Flutter framework encourages.
That was initially very non-intuitive compared to the imperative approach.
Still, this approach has worked for me over time, and I understand that it has many advantages over the imperative approach.

To my surprise, I practically tried to perform usability testing, which went very well overall.
The testers understood most of the tasks and performed them very well.
The game came to them visually, not bloated, and easy to understand.
The testers even found a few minor bugs or tips for improvement, but one critical bug.

According to the usability of the prototype testing and the fulfilled goals of the work, I evaluate that the created game has potential that could be used more in later improvements.

\section{Ideas on Future Development}

The potential of the developed game could be used more, especially after further processing and better graphic and musical styling, and the addition of more story and educational material.
The game can also be used in primary schools or secondary schools to introduce programming and programming concepts.

Not-to-be-implemented features have already been analyzed in the chapter \ref{analysis:game:future-features}.
However, all the features are exciting and would add other vital elements to the game.

In addition, and from experience gained from the development and response of testers, more improvements could expand the game.
One idea is that block visual programming, as seen in the game mission, may not be the only concept of the game.
Therefore, other types of missions could be added to the game, where, for example, the player would directly perform a logical puzzle by clicking, moving, etc.
Thus, a universal system for puzzles could be created that would allow them to be generated and checked using pre-prepared configurations.
Another type of mission could be with circuit and gate concepts, i.e., the use of \mintinline{text}{and}, \mintinline{text}{or}, \mintinline{text}{not}, or \mintinline{text}{xor} gates to achieve the desired output result.

One of the first extensions could and should be to improve the game's graphics and unique look-and-feel styling.
Apart from the game mission, the current form of the game has a not very interesting look.
Although the game consists of tutorials, the passage through the screens could be improved, for example, by using graphic elements and images that would color the game and create a pleasant atmosphere.
Related to this is the passage of missions that are far too separate.
Ideally, the game should be improved so that players can connect directly between missions, i.e., adding the \textquote*{next} button to the mission screens.

There are many ideas for expanding this game.
Some ideas focus on looks, others on game options.
Therefore, the game's future development is straightforward -- gradually implement all appropriate improvements.

\end{conclusion}
