\section{Second Phase}

As in the~first phase, the~moderator and testers gradually made a~video call using Microsoft Teams.
Each tester was acquainted with the~process and purpose of testing.
They were explained and advised that they should share their idea aloud and that they should also read the~tasks aloud and, if necessary, reformulate them in their own words.
They were informed that the~moderator would monitor their actions and not actively communicate so as not to interfere with their decisions.
Each tester was sent a~task assignment in the~chat.

The~second testing phase was attended by representatives of children, parents, and teachers.
These testers were assigned a~five-digit code for anonymization and the~possibility of reference to specific testers in the~text.
The~testers \mintinline{text}|2df9c|, \mintinline{text}|93750|, \mintinline{text}|a5961|, and \mintinline{text}|84152| took part in the~second testing.

Unlike the~first phase, the~game mission's description was displayed\linebreak{}immediately after launch.
A description of the~\mintinline{text}|size| and \mintinline{text}|speed| attributes has also been added into the~learning mission.

\subsection*{Task 1}

The~first task was to sign in to the~game, i.e., create an~account.
This task was not a~problem for any testers; everything was without problems.

\subsection*{Task 2}

The~second task was to go to the~game's main screen and then navigate to the~profile screen.

This task was also very easy for all testers.
In addition, tester \mintinline{text}|2df9c| recommended that the~application name serves as a~button on the~main page for more applications and games, but would like to highlight it more because it looks just like any other text.
Testers \mintinline{text}|84152| would like to have the~name of the~currently signed-in player in addition to the~avatar icon in the~menu.

\subsection*{Task 3}

The~third task was to find a~course screen and search for a~course that contained three missions.
They should then read the~name of this course.

This task was also successful for all testers.
However, tester \mintinline{text}|a5961|, at first, did not realize that \textquote*{stories} were the~courses they were looking for.
Even so, everyone found the~screen they were looking for in the~end.

\subsection*{Task 4}

The~fourth task was to find out which missions the~story contained.
The~task was also to describe and explain how different mission graphics affect them and what they think they represent.

The~testers completed this task without any problems.
They all understood what missions are and their meaning according to the~graphics used.

\subsection*{Task 5}

The~fifth task was to open learning missions and read them.

This task was also easy for everyone.
Everyone went through the~missions and understood the~meaning of the~story and the~explanation of the~commands of the~game mission.

\subsection*{Task 6}

The~sixth task concerns the~game itself.
The~goal is to open a~game mission and complete several subtasks.
They were to read the~description, explain how they understood it, and use a~visual programming tool to accomplish the~task.

As in the~first testing phase, the~task was more difficult for testers.
\linebreak
However, they all completed the~mission.

\pagebreak

Testers \mintinline{text}|2df9c|, \mintinline{text}|93750| and \mintinline{text}|a5961| had trouble adding blocks to the~bottom of the~command list.
The~problem was with the~addition itself when the~area to be added was too small, and the~testers dropped the~blocks as if outside, albeit visually close.
Another problem was when a~tester used the~entire height of the~panel, had to scroll down, and had to scroll again after adding.
So the~problem was, or rather the~expectation, that the~panel would scroll automatically if the~user dragged the~block and pulled it down.
A similar problem with scrolling was when selecting the~direction when part of the~menu overlay overflows the~bottom of the~window, and the~player had to scroll complicatedly. Even then, the~selection was not entirely straightforward.

Tester \mintinline{text}|2df9c| also did not understand what marks are and what their meaning is.
Tester \mintinline{text}|84152| still had trouble understanding \mintinline{text}|size| and \mintinline{text}|speed| attribute, and suggested that the~post-game dialog could also contain some help.

Tester \mintinline{text}|93750| also discovered an~error while starting the~game when the game tried to process an~empty \mintinline{text}|while| command block, which caused an\linebreak{}endless loop, which prevented the~completion of queue processing.

\subsection*{Task 7}

The~seventh task was to go to the~statistics screen and determine which missions were completed.

Completing this mission was not a~problem for the~testers, and everyone completed the~task.
The~tester \mintinline{text}|2df9c|, like another tester in the~first phase, first confused mission and story.

\subsection*{Task 8}

The~eighth task was to empathize with a~journalist looking for information.
The~task was to get to the~page intended for them.

All testers completed this task without any problems.
Testers \mintinline{text}|a5961| and \mintinline{text}|84152| mentioned that they would welcome a~special button in the~bottom menu.

\subsection*{Task 9}

The~ninth task was to sign out of the~game and navigate to the~sign-in screen.

All testers managed to complete this task.
Tester \mintinline{text}|93750| was not sure about the~sign-in icon that they did not understand, but they understood what to do.
In conclusion, tester \mintinline{text}|a5961| would welcome a~video tutorial or overlay tutorial.

\pagebreak

\subsection*{Identified Shortcomings}

The~second phase of testing confirmed that displaying the~description of the~game mission immediately after launch is more appropriate.
A critical error was also found in processing blocks into the~executable queue, where the~program made an~endless loop.
This bug has been fixed.
In addition, no other errors were found.
Players had less trouble understanding \mintinline{text}|size| and \mintinline{text}|speed| attributes, but it would probably be better to add some form of explanation to the~dialog.
