\section{Motivation}

I have enjoyed playing computer games from an early age.
Although most of my friends exclusively played non-educational games or games where one did not need to think, I always enjoyed the puzzle, strategic, building, and educational games.
Even today, I remember how I and my sister both played together game \emph{Alík - Veselá matematika} to practice the basics of mathematics.
This game was enjoyable, even though it was an educational game.
The main reason was that it had some story, and it did not feel like learning.
It felt like playing a video game.
You needed to compute some numbers to move or help some character in the game.
After completing a task, you receive some points, and I think using them, you could acquire some toys for your in-game collection.

These concepts sound like gamification to me, and I would like to create a prototype for a game that will teach children the basics of programming concepts, so maybe some children, like me years prior, will enjoy their time learning a bit more.

I have been helping with organizing summer camps and other events for children with a local organization for years.
We prepare activities and games for children to enjoy the time and learn something new.
I also have experience educating children and adults while writing technical articles and lecturing about programming.
I always try to present relevant information in the most friendly form in all my articles and lectures.
In the future, I would like to focus on developing an educational project or teaching.
