% arara: xelatex: { shell : yes }
% arara: biber
% arara: xelatex: { shell : yes }
% arara: xelatex: { synctex: 1, shell : yes }

\documentclass[thesis=M,english]{template/FITthesis}[2019/12/23]
\usepackage[utf8]{inputenc} % LaTeX source encoded as UTF-8
\usepackage{dirtree}
\usepackage{xevlna}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{blindtext}

\makeatletter
\newcommand\my@hyphen{-}
\newcommand\my@apostroph{'}
\patchcmd\select@language{-}{\my@hyphen }{}{\fail}
\patchcmd\select@language{'}{\my@apostroph }{}{\fail}
\makeatother

\usepackage[style=iso-numeric,backend=biber]{biblatex}
\addbibresource{library.bib}

\usepackage{minted}
\counterwithin{listing}{chapter}
%\renewcommand{\listingscaption}{Výpis kódu}
%\renewcommand{\listoflistingscaption}{Seznam výpisů kódu}

\usepackage{lineno}
\usepackage{csquotes}
\usepackage{placeins}
\usepackage{suffix}

\input{macros/_all.tex}

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
% SETTINGS
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 

\department{Department of Software Engineering}
\title{King Karel -- An~Educational Programming Puzzle Game}
\authorGN{Jan} %(křestní) jméno (jména) autora
\authorFN{Bittner} %příjmení autora
\authorWithDegrees{Bc. Jan Bittner} %jméno autora včetně akademických titulů
\author{Jan Bittner} %jméno autora bez akademických titulů
\supervisor{Ing. Jan Matoušek}
\acknowledgements{Throughout the~writing of this thesis I~have received a~great deal of support and assistance.
\\\\
First and foremost,
I~would like to express my deep gratitude to my~supervisor,
Ing.~Jan Matoušek.
I~am incredibly grateful for our friendly chats
and his dedicated support and guidance.
\\\\
I~want to acknowledge my colleagues from the~FIT Discord community for their tremendous support throughout my studies.
Their regular dose of memes often improved my mood.
It has been an~honor to serve beside you.
\\\\
Last but not least,
I~owe more than thanks to my family and friends
for providing me with unfailing support and continuous encouragement throughout my years of study and through the~process of writing this thesis. This accomplishment would not have been possible without them. Thank you.
}
\abstractCS{Magisterská práce se zabývá vývojem prototypu hry King Karel,
logické hry na výuku programování.
Práce popisuje proces analýzy, návrhu a~implementace zmiňované hry s důrazem na návrh architektury jednotlivých částí.
Klientská část je tvořena pomocí frameworku Flutter a~serverová část je tvořena pomocí frameworku ASP.NET Web API.
}
\abstractEN{The~master's thesis deals with the~development of a~prototype of the~game King Karel~--
an educational programming puzzle game.
The~thesis describes the~process of analysis, design, and implementation of the~mentioned game,
emphasizing the~design of the~architecture of individual parts.
The~client part is created using the~Flutter framework,
and the~server part is created using the~ASP.NET Web API framework.
}
\placeForDeclarationOfAuthenticity{Prague}
\declarationOfAuthenticityOption{2} %volba Prohlášení
\keywordsCS{výuková hra, web, desktop, Flutter, C\#, programovací\linebreak{}logická hra, multiplatformní framework}
\keywordsEN{educational game, web, desktop, Flutter, C\#, programming puzzle, cross-platform framework}
\website{https://github.com/tenhobi/masters-thesis} %volitelná URL práce, objeví se v tiráži

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % 
% OBSAH
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % %  

\begin{document}
\overfullrule=30pt

\input{chapters/_all.tex}

{
    \setlength{\emergencystretch}{3em} 
    \printbibliography
}

\appendix
\input{parts/appendix/_all.tex}

\end{document}
